---
title: "bee_sample_script"
author: "Moganavalli Kattan"
date: "2023-11-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Daily mean temperature

#Process data

Calculate daily mean of stations
```{r}
dmt_base_df <- dmt_base_df %>%
  rename("Date" = "datetime_swedish")
dmt_base <- temp_base %>%
  group_by (Date) %>%
  summarise(dmt_base_temp = mean(air_temp))
write.csv(dmt_base, file = "dmt_base.csv")

dmt_middle <- temp_middle %>%
  group_by (Date) %>%
  summarise(dmt_middle_temp = mean(air_temp))
write.csv(dmt_middle, file = "dmt_middle.csv")

dmt_summit <- temp_base %>%
  group_by (Date) %>%
  summarise(dmt_summit_temp = mean(air_temp))
write.csv(dmt_summit, file = "dmt_summit.csv")
```

Rename columns
```{r}
dmt_sum_df <- dmt_sum_df %>%
  rename("dmt_summit_temp" = "summit_temp")

#remove outliers
dmt_sum_df <- subset(dmt_sum_df, dmt_sum_df$dmt_summit_temp > -25)

dmt_mid_df <- dmt_mid_df %>%
  rename("dmt_middle_temp" = "middle_temp")

dmt_base_df <- dmt_base_df %>%
  rename("Date" = "datetime_swedish") %>%
  rename("dmt_base_temp" = "base_temp")
```

Merge
```{r}
dmt_stations <- seq.Date(from = as.Date("2018-04-01"),
        to = as.Date("2022-09-30"),
        by = "day")  %>%
  data.frame(Date = .)
dmt_stations <- left_join(dmt_stations, dmt_base_df, by = "Date")
dmt_stations <- left_join(dmt_stations, dmt_mid_df, by = "Date")
dmt_stations <- left_join(dmt_stations, dmt_sum_df, by = "Date")
dmt_stations <- dmt_stations[months(dmt_stations$Date) %in% month.name[4:9],]
#sum and mid only missing some dates (<08/2019, 09/2022)
```

#How temperature changes over time
```{r}
dmt_stations <- dmt_stations %>%
  mutate(diff_temp = dmt_base_temp - dmt_summit_temp)

dmt_stations %>%
  filter(Date >= "2022-01-01")%>%
  ggplot(aes(x = Date, y = diff_temp)) +
  geom_point(width = 0.1)+
  geom_smooth(method = lm, se = TRUE, formula = y ~ x)+
  xlab("Time of year") + 
  ylab("Temperature (°C)")+
  theme_classic()

pdf(file = "station_temp.pdf", width = 10, height = 6)

dmt_stations %>%
  filter(Date >= "2022-01-01")%>%
  ggplot() +
  geom_line(aes(x = Date, y = dmt_summit_temp, colour = "summit"))+
  geom_line(aes(x = Date, y = dmt_middle_temp, colour = "middle"))+
  geom_line(aes(x = Date, y = dmt_base_temp, colour = "base"))+
  xlab("Time of year") + 
  ylab("Temperature (°C)")+
  theme_classic()

dev.off()

```
The difference between the stations remains constant

#find intercept between stations
```{r}
#base and summit station
A <- dmt_stations %>%
  ggplot(aes(x = dmt_base_temp, y = dmt_summit_temp)) +
  geom_point(width = 0.1)+
  geom_smooth(method = lm, se = TRUE, formula = y ~ x)+
  xlab("Daily mean temperature at base station (°C)") + 
  ylab("Daily mean temperature at summit station (°C)")+
  theme_classic()



dmt_bs_lm <- lm(dmt_summit_temp ~ dmt_base_temp, data = dmt_stations)

par(mfrow = c(2,2))
    plot(dmt_bs_lm)
    
summary(dmt_bs_lm)
```
There is a significant relationship between the base and summit dmts (y =  +  x, R-squared: , F = , d.f. = ,, p ).


```{r}
#base and middle station
B <- dmt_stations %>%
  ggplot(aes(x = dmt_base_temp, y = dmt_middle_temp)) +
  geom_point(width = 0.1)+
  geom_smooth(method = lm, se = TRUE, formula = y ~ x)+
  xlab("Daily mean temperature at base station (°C)") + 
  ylab("Daily mean temperature at middle station (°C)")+
  theme_classic()

dmt_bm_lm <- lm(dmt_middle_temp ~ dmt_base_temp, data = dmt_stations)

par(mfrow = c(2,2))
    plot(dmt_bm_lm)
    
summary(dmt_bm_lm)

```
There is a significant relationship between the base and middle dmts (y =  +  x, R-squared: , F = , d.f. = ,, p ).


```{r}
#middle and summit station
C <- dmt_stations %>%
  ggplot(aes(x = dmt_middle_temp, y = dmt_summit_temp)) +
  geom_point(width = 0.1)+
  geom_smooth(method = lm, se = TRUE, formula = y ~ x)+
  xlab("Daily mean temperature at middle station (°C)") + 
  ylab("Daily mean temperature at summit station (°C)")+
  theme_classic()

dmt_ms_lm <- lm(dmt_summit_temp ~ dmt_middle_temp, data = dmt_stations)

par(mfrow = c(2,2))
    plot(dmt_ms_lm)
    
summary(dmt_ms_lm)
```
There is a significant relationship between the base and middle dmts (y =  +  x, R-squared: , F = , d.f. = ,, p ).

```{r}
pdf(file = "rates.pdf", width = 15, height =5)
A + B + C + plot_layout(ncol = 3) + plot_annotation(tag_levels = "A")
dev.off()
```


#Calculate rates of temperature change with altitude:
Alt[base] = .392
Alt[mid] = .699
Alt[sum] = 1.169
delta bs = .777
delta bm = .307
delta ms = .470
rate = (c/delta) in degrees per km
intercept = coefficients(TO_0_pgls)[1]
```{r}
#bs
rate_bs <- (coefficients(dmt_bs_lm)[1]/0.777)
rate_bs
  
#bm
rate_bm <- (coefficients(dmt_bm_lm)[1]/0.307)
rate_bm
  
#ms
rate_ms <- (coefficients(dmt_ms_lm)[1]/0.470)
rate_ms

```

#match temperature and bee observation data
```{r}
bee_macro <- bee_macro %>%
  mutate(air_temp = case_when(
    Date <=	"2018-07-20" ~ (air_temp = summit_temp + ((rate_bs/1000) * (Altitude-1169))),
    (Date <=	"2019-06-18" | (Date >= "2022-09-21" & Date <= "2022-09-25") | Date == "2022-09-28" | Date == "2022-09-29") ~ (air_temp = base_temp + ((rate_bs/1000) * (Altitude-392))),
    Altitude <= "690.45" ~ (air_temp = middle_temp + ((rate_bm/1000) * (Altitude-699))),
    Altitude >= "748.85" ~ (air_temp = middle_temp + ((rate_ms/1000) * (Altitude-699)))
    ))

sum(is.na(bee_macro$air_temp))
```

###Visualise data and run analyses

Species temperature preference
```{r}
D <- bee_macro %>%
  mutate(class = fct_reorder(Bombus_Species, air_temp, .fun = 'mean'))%>%
  ggplot(aes(x = reorder(Bombus_Species, air_temp), y = air_temp, colour = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
    colour = "black", width = 0.1, 
    position = position_nudge(x = 0.15)) +
  stat_summary(fun = mean, geom = "point", 
    colour = "black", size = 3, 
    position = position_nudge(x = 0.15)) + 
  xlab("") +  
  ylab("Temperature (°C)")+
  coord_flip()+
  theme_classic()+
  theme(axis.text.y = element_text(face = 'italic'))



temp_lm <- lm(air_temp ~ Bombus_Species, data = bee_macro)

par(mfrow = c(2,2))
    plot(temp_lm)
    
anova(temp_lm)

summary(temp_lm)
```

There was a significant correlation between mean Temperature and Bombus_Species (GLS: R-squared: , F = , df = , , p ).

##ITD Analyses

Comparing mean temp to intertegular distance (ITD)
```{r}
mean_ITD_df <- bee_macro %>%
  filter(!is.na (Intertegular_distance_cm)) %>%
  group_by(Bombus_Species) %>%
  summarise (mean_ITD = mean(Intertegular_distance_cm))

ITD_mean_temp_df <- left_join(mean_ITD_df, tempsummary, by = "Bombus_Species")

X <- ITD_mean_temp_df %>%
  ggplot(aes(x = mean_ITD, y = mean_temp, colour = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_point(width = 0.1, size = 10 , show.legend = FALSE)+
  xlab("Mean intertegular distance (cm)") + 
  ylab("Mean temperature (°C)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()


ITD_lm <- lm(mean_temp ~ mean_ITD, data = ITD_mean_temp_df)

par(mfrow = c(2,2))
    plot(ITD_lm)
    
summary(ITD_lm)
```
There is not a significant linear relationship between the mean temperature of species occurrence and mean species ITD (LM: R-squared: , F=, d.f.=,, p = ).


#calculating temperature and altitude in future scanarios
Scenario 1
2050 +0.4
2100 +0.3
Scenario 2
2050 +0.4
2100 +0.7
Scenario 3
2050 +0.4
2100 +1.6
Scenario 4
2050 +0.4
2100 +2.5
Scenario 5
2050 +0.5
2100 +3.3

From bee data
+delta temp to air_temp
```{r}
bee_macro <- bee_macro %>%
  mutate(temp_SSP_50 = air_temp + 0.4)

bee_macro <- bee_macro %>%
  mutate(temp_SSP5.8.5_50 = air_temp + 0.5)

bee_macro <- bee_macro %>%
  mutate(temp_SSP1.1.9_100 = air_temp + 0.3)

bee_macro <- bee_macro %>%
  mutate(temp_SSP1.2.6_100 = air_temp + 0.7)

bee_macro <- bee_macro %>%
  mutate(temp_SSP2.4.5_100 = air_temp + 1.6)

bee_macro <- bee_macro %>%
  mutate(temp_SSP3.7.0_100 = air_temp + 2.5)

bee_macro <- bee_macro %>%
  mutate(temp_SSP5.8.5_100 = air_temp + 3.3)
```
These are the temperatures at the current altitudes at which the bee was found


use new temp and alt to calculate new alt at which air_temp can be found
```{r}
bee_macro <- bee_macro %>%
  mutate(alt_SSP_50 = Altitude - (400/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP5.8.5_50 = Altitude - (500/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP1.1.9_100 = Altitude - (300/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP1.2.6_100 = Altitude - (700/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP2.4.5_100 = Altitude - (1600/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP3.7.0_100 = Altitude - (2500/rate_bs))

bee_macro <- bee_macro %>%
  mutate(alt_SSP5.8.5_100 = Altitude - (3300/rate_bs))
```

#calculate and plot the impact (% population loss) under climate scenarios
1
```{r}
temp1_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP_50 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp1_impact = mean(satisfies) * 100)

alt1_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP_50 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt1_impact = mean(satisfies) * 100)
```
2
```{r}
temp2_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP5.8.5_50 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp2_impact = mean(satisfies) * 100)

alt2_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP5.8.5_50 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt2_impact = mean(satisfies) * 100)
```
3
```{r}
temp3_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP1.1.9_100 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp3_impact = mean(satisfies) * 100)

alt3_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP1.1.9_100 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt3_impact = mean(satisfies) * 100)
```
4
```{r}
temp4_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP1.2.6_100 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp4_impact = mean(satisfies) * 100)

alt4_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP1.2.6_100 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt4_impact = mean(satisfies) * 100)
```
5
```{r}
temp5_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP2.4.5_100 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp5_impact = mean(satisfies) * 100)

alt5_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP2.4.5_100 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt5_impact = mean(satisfies) * 100)
```
6
```{r}
temp6_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP3.7.0_100 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp6_impact = mean(satisfies) * 100)

alt6_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP3.7.0_100 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt6_impact = mean(satisfies) * 100)
```
7
```{r}
temp7_impact_df <- bee_macro %>%
  group_by(Bombus_Species) %>%
  mutate(upper_limit = max(air_temp)) %>%
  mutate(satisfies = case_when(
		temp_SSP5.8.5_100 > upper_limit ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(temp7_impact = mean(satisfies) * 100)

alt7_impact_df <- bee_macro %>%
  mutate(satisfies = case_when(
		alt_SSP5.8.5_100 > 1169 ~ 1,
		.default = 0)) %>%
	group_by(Bombus_Species) %>% 
	summarise(alt7_impact = mean(satisfies) * 100)
```

```{r}
tempall_impact_df <- left_join(temp1_impact_df, temp2_impact_df, by = "Bombus_Species")
tempall_impact_df <- left_join(tempall_impact_df, temp3_impact_df, by = "Bombus_Species") 
tempall_impact_df <- left_join(tempall_impact_df, temp4_impact_df, by = "Bombus_Species") 
tempall_impact_df <- left_join(tempall_impact_df, temp5_impact_df, by = "Bombus_Species") 
tempall_impact_df <- left_join(tempall_impact_df, temp6_impact_df, by = "Bombus_Species") 
tempall_impact_df <- left_join(tempall_impact_df, temp7_impact_df, by = "Bombus_Species") 
  
altall_impact_df <- left_join(alt1_impact_df, alt2_impact_df, by = "Bombus_Species")
altall_impact_df <- left_join(altall_impact_df, alt3_impact_df, by = "Bombus_Species") 
altall_impact_df <- left_join(altall_impact_df, alt4_impact_df, by = "Bombus_Species") 
altall_impact_df <- left_join(altall_impact_df, alt5_impact_df, by = "Bombus_Species") 
altall_impact_df <- left_join(altall_impact_df, alt6_impact_df, by = "Bombus_Species") 
altall_impact_df <- left_join(altall_impact_df, alt7_impact_df, by = "Bombus_Species") 
```

```{r}
S1_temp <- left_join(temp1_impact_df, temp3_impact_df, by = "Bombus_Species")
S1_temp <- S1_temp %>%
  rename("2050" = "temp1_impact")%>%
  rename("2100" = "temp3_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S2_temp <- left_join(temp1_impact_df, temp4_impact_df, by = "Bombus_Species")
S2_temp <- S2_temp %>%
  rename("2050" = "temp1_impact")%>%
  rename("2100" = "temp4_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S3_temp <- left_join(temp1_impact_df, temp5_impact_df, by = "Bombus_Species")
S3_temp <- S3_temp %>%
  rename("2050" = "temp1_impact")%>%
  rename("2100" = "temp5_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S4_temp <- left_join(temp1_impact_df, temp6_impact_df, by = "Bombus_Species")
S4_temp <- S4_temp %>%
  rename("2050" = "temp1_impact")%>%
  rename("2100" = "temp6_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S5_temp <- left_join(temp2_impact_df, temp7_impact_df, by = "Bombus_Species")
S5_temp <- S5_temp %>%
  rename("2050" = "temp2_impact")%>%
  rename("2100" = "temp7_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))
```

```{r}
AO <-  S1_temp %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP1-1.9 (very low)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()

AP <-  S2_temp %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP1-2.6 (low)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
  
AQ <-    S3_temp %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP2-4.5 (intermediate)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
    
 AR <-     S4_temp %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP3-7.0 (high)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
      
 AS <-       S5_temp %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP5-8.5 (very high)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()

```

```{r}
S1_alt <- left_join(alt1_impact_df, alt3_impact_df, by = "Bombus_Species")
S1_alt <- S1_alt %>%
  rename("2050" = "alt1_impact")%>%
  rename("2100" = "alt3_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S2_alt <- left_join(alt1_impact_df, alt4_impact_df, by = "Bombus_Species")
S2_alt <- S2_alt %>%
  rename("2050" = "alt1_impact")%>%
  rename("2100" = "alt4_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S3_alt <- left_join(alt1_impact_df, alt5_impact_df, by = "Bombus_Species")
S3_alt <- S3_alt %>%
  rename("2050" = "alt1_impact")%>%
  rename("2100" = "alt5_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S4_alt <- left_join(alt1_impact_df, alt6_impact_df, by = "Bombus_Species")
S4_alt <- S4_alt %>%
  rename("2050" = "alt1_impact")%>%
  rename("2100" = "alt6_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))

S5_alt <- left_join(alt2_impact_df, alt7_impact_df, by = "Bombus_Species")
S5_alt <- S5_alt %>%
  rename("2050" = "alt2_impact")%>%
  rename("2100" = "alt7_impact")%>%
  mutate("2020" = 0)%>%
  pivot_longer(!Bombus_Species, names_to = "year", values_to = "impact")%>%
  mutate(year = as.integer(year))
```


```{r}
AT <-  S1_alt %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP1-1.9 (very low)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()

AU <-  S2_alt %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP1-2.6 (low)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
  
AV <-    S3_alt %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP2-4.5 (intermediate)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
    
AW <-      S4_alt %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP3-7.0 (high)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()
      
AX <-        S5_alt %>%
  ggplot(aes(x = year, y = impact, colour = Bombus_Species, group = Bombus_Species)) +
  scale_color_manual(values = c("#C49AA6", "#7B8B59", "#FEE5B3", "#AEDFF9", "#EBAE9D", "#C1E1D9", "#FABD9E", "#BAA8D8", "#799AC0", "#E8B6AB", "#F4C259", "#A4B996", "#BFA58C", "#6F93A4", "#84A67D"))+
  geom_line(width = 0.1) +
  scale_x_continuous(breaks = c(2020, 2050, 2100))+
  xlab("Year") + 
  ylab("Individuals lost per species (%)")+
  ylim(0, 100)+
  ggtitle("SSP5-8.5 (very high)")+
  guides (colour = guide_legend(title = "Bombus species"))+
  theme_classic()

```